---
title: "R Markdown Demo"
author: "Lewis Mews"
date: "2 July 2018"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(gridExtra)
data <- read.csv("Data/nfl.csv")

```


# Introduction

This is a demo markdown created for the __Colchester R Users Group__ meetup. This Demo can be downloaded from `Gogs` using this link <http://obj-vs-efactory:3000/lmews/Colchester_R_Users_Group_Demo>. 


In this R Markdown file I will

1) Plot some of the data 
2) Look at a basic linear model
3) Get a summary of the results

The Data used will be NFL data with the following variables

* Division
* Total Yards For and Against
* Total Points For and Against
* Wins

# Methods

<br>

#### Step 1) 
Firstly I looked at what data we have

``` {r head_data, fig.align='center', fig.height=9}

head(data)

```

<br>

#### Step 2) 
Next I plotted the data to get see if there was any interesting relationships

``` {r initial_plot, fig.align='center', fig.height=9}

p1 <- ggplot(data) + aes(x = Total.Yards.Offense, y = Wins) + geom_point() + ggtitle("Total Yards Offense") + theme(plot.title = element_text(hjust = 0.5))
p2 <- ggplot(data) + aes(x = Total.Points.offense, y = Wins) + geom_point() + ggtitle("Total Points Offense") + theme(plot.title = element_text(hjust = 0.5))
p3 <- ggplot(data) + aes(x = Total.Yards.Defense, y = Wins) + geom_point() + ggtitle("Total Yards Defense") + theme(plot.title = element_text(hjust = 0.5))
p4 <- ggplot(data) + aes(x = Total.Points.Defense, y = Wins) + geom_point() + ggtitle("Total Points Defense") + theme(plot.title = element_text(hjust = 0.5))
p5 <- ggplot(data) + aes(x = Total.Yards.Offense-Total.Yards.Defense, y = Wins) + geom_point() + ggtitle("Total Net Yards") + theme(plot.title = element_text(hjust = 0.5))
p6 <- ggplot(data) + aes(x = Total.Points.offense-Total.Points.Defense, y = Wins) + geom_point() + ggtitle("Total Net Points") + theme(plot.title = element_text(hjust = 0.5))

grid.arrange(p1, p2, p3, p4, p5, p6, ncol = 2)

```

<br>

#### Step 3) 
I then created a simple linear model of wins against total defensive points and total offensive points 

``` {r model, fig.align='center', fig.height=9}

(model <- lm(Wins ~ Total.Points.offense + Total.Points.Defense, data=data))

```

# Results

Here is a summary of the regression model:

``` {r summarise_model}
summary(model)

```
<br>
Below shows a plot of fitted values vs actual values

``` {r plot_model}
plot(round(model$fitted.values), data$Wins)

```

# Conclusion

so the final model is:

$$E(Wins) = `r model$coefficients[1]` + `r model$coefficients[2]`*Total.Points.offense `r model$coefficients[3]`*Total.Points.Defense$$

As can be seen, the model performs terribly. 